The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-01-04 paper/paper.tex
more content

In this paper we discuss and evaluate methods for assigning objects to tomographic bins, and 
specifically the impact
of using a limited set of color bands to make those assignments, motivated by requirements of using the
metacalibration method for galaxy shape measurement to limit biases.  Tomographic methods have been 
explored before in \citet{jain} and \citet{kitching2019}.  In this paper we describe the results of a 
challenge using simulated Rubin-like data with a range of methods submitted by different teams.

@@

\url{https://arxiv.org/abs/1901.06495}

\url{https://arxiv.org/abs/astro-ph/0609338}

@@

\subsection{Philosophy}
\begin{itemize}
    \item Simplest challenge (optimistic data)
    \item Openness?
    \item Science-relevant metrics
    \item Performance at scale
\end{itemize}

\subsection{Data}

@@

@@

>>>>

In this paper we discuss and evaluate methods for assigning objects to tomographic bins, and 
specifically the impact
of using a limited set of color bands to make those assignments, motivated by requirements of using the
metacalibration method for galaxy shape measurement to limit biases.  Tomographic methods have been 
explored before in \citet{jain} and \citet{kitching2019}.  In this paper we describe the results of a 
challenge using simulated Rubin-like data with a range of methods submitted by different teams.  We explore how many tomographic bins we can effectively generate using only a subset of bins, and compare methods submitted to the challenge.

@@

@@

The Dark Energy Science Collaboration (DESC) Tomographic Challenge was launched in May 2019 and 
advertised among the LSST cosmology community, though it was open to outside entrants.

In the challenge, participants assigned simulated galaxies to tomographic bins,
using only their (g)riz bands and associated errors.  Their goal was to maximize the cosmological
information in the final split data set; this is generally acheived by separating different bins by 
redshift as much as possible.  Particpants were free to optimize or simply select nominal (target) 
redshift bin edges from their training sample, but in either case had to classify galaxies into the 
different bins.

\subsection{Philosophy}

Since this was a preliminary challenge designed to explore whether it is possible \emph{in theory}
to use only (g)riz for tomography, we chose to simplify several aspects of the data.  In realistic 
situations we will have access to limited sized training sets for WL photometric redshifts, since 
spectra are time-consuming to obtain.  These training sets will also be highly incomplete compared
to full catalogs, especially at faint magnitudes where spectroscopic coverage is sparse.  In this
challenge we avoided both these issues -- the training samples we provided (see below) were comparable
in size to the testing sample, and drawn from the same population.  Given this, the challenge
represents a best-case scenario -- if no method succeeded on this easier case then more realistic
cases would probably be impossible.

Despite these simplifications, the other aspects of the challenge and process were designed to be
as directly relevant as possible to the particular WL science case we focus on.  The data set
was chosen to mimic the population, noise, and cuts we will use in real data (see \autoref{sec:data}, 
and the metrics were designed to be as close to the science goals as possible, rather than a lower
level representation (see \autoref{sec:metrics}). The data set was also large enough to pose a 
reasonably realistic test of methods at the large data volume required for upcoming surveys, where
$10^9$ -- $10^{10}$ galaxies will be measured.

The challenge was open to any entrants, not just those already involved in DESC, but it was
advertised primarily through Rubin, and so is perhaps best described as semi-public.
Participants tested and ran their methods locally, but submitted code to be run as part of a central
combined analysis.  No prize was offered apart from recognition.

\begin{itemize}
    \item Performance at scale
\end{itemize}

\subsection{Data}
\label{sec:data}

@@

In this challenge we use only a source (background) population, since the metacal requirements
do not apply to the foreground lens sample. We do, however, calculate

@@

\appendix{Mistakes}
The challenge organizers made a number of mistakes when building and running the challenge.
These do not invalidate the process in any way, but we describe them here in the hope of
being useful for future challenge designers.

\begin{itemize}
    \item Infrastructure for checking submissions
    \item Guidance for users regarding caching and batch processing
    \item Timing
    \item Training set size
    \item Advertisement
\end{itemize}
